---
title: "December of 2020's Highs"
output: html_notebook
---

#### Data was pulled from the NWS Omaha.

```{r warning=FALSE,message=FALSE,echo=FALSE}
# Loading Libraries
library(readr)
library(dplyr)
library(xts)
library(dygraphs)
```

```{r message=FALSE,echo=FALSE}
# craft data frame
temps <- read.csv("weather.csv")
rownames(temps) = as.Date(as.character(temps$date), "%Y%m%d")
```

```{r}
graph_it <- as.xts(temps[-1])
dygraph(xts_temps, main = "Highs and Lows of the Month of December, 2020") %>%
  dyAxis("y", label = "Degrees Fahrenheit") %>%
  dySeries("V2", label = "Highs") %>%
  dySeries("V3", label = "Lows")
```
## Table of Highs, Lows, and Averages
All temps in Fahrenheit. Sorry Metric World.
```{r}
tempscht <- temps %>%
  mutate(avg_temp = (high + low)/2) %>%
  rename("Date" = date, "Highs" = high, "Lows" = low, "Daily Avg" = avg_temp)
tempscht
```
## Almanac vs NWSOmaha

The Old Farmer's Almanac 2021's December Average High Prediction is 33.5°F. Meanwhile, the calculated average high from NWS Omaha predictions is `r average_high <- mean(temps[,2]);average_high`°F. It appears the astrometeorological prediction is below the observations of the NWS Office at Valley, NE.