---
title: "December of 2020's Highs"
output: html_notebook
params:
  a: 33.5
  b: !r mean(c(49,46,47,54,49,36,53,58,61,52,38,32,27,21))
---

#### Data was pulled from the NWS Omaha.

```{r warning=FALSE,message=FALSE,echo=FALSE}
# Loading Libraries
library(readr)
library(dplyr)
library(xts)
library(dygraphs)
```

```{r message=FALSE,echo=FALSE}
# craft data frame
dates <- c("2020-12-01","2020-12-02","2020-12-03","2020-12-04","2020-12-05","2020-12-06","2020-12-07","2020-12-08","2020-12-09","2020-12-10","2020-12-11","2020-12-12","2020-12-13","2020-12-14")
hi_temps <- c(49,46,47,54,49,36,53,58,61,52,38,32,27,21)
lo_temps <- c(18,21,20,24,22,24,24,24,31,27,32,20,16,8)
temps <- data.frame(
  date = dates,
  high_in_f = hi_temps,
  low_in_f = lo_temps,
  stringsAsFactors = FALSE
)
```

```{r echo=FALSE}
zoo_temps <- (read.zoo("weather.csv", index.column = 1, sep=",", format="%Y-%m-%d"))
xts_temps <-as.xts(zoo_temps)
dygraph(xts_temps, main = "Highs and Lows of the Month of December, 2020") %>%
  dyAxis("y", label = "Degrees Fahrenheit") %>%
  dySeries("V2", label = "Highs") %>%
  dySeries("V3", label = "Lows")
```
## Table of Highs, Lows, and Averages
All temps in Fahrenheit. Sorry Metric World.
```{r echo=FALSE}
tempscht <- temps %>%
  mutate(avg_temp = (high_in_f + low_in_f)/2) %>%
  rename("Date" = date, "Highs" = high_in_f, "Lows" = low_in_f, "Daily Avg" = avg_temp)
tempscht
```
## Almanac vs NWSOmaha

The Old Farmer's Almanac 2021's December Average High Prediction is `r params$a`°F. Meanwhile, the calculated average high from NWS Omaha predictions is `r params$b`°F. It appears the astrometeorological prediction is below the observations of the NWS Office at Valley, NE.